---
title: "Holding ourselves accountable for data management: actions in Alaska"
author: "McCrea Cobb, Amy Pocewicz, Erik Osnas, and Ryan Wilson"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["css/xaringan-themer.css", "css/my-theme.css"]
    nature:
      ratio: "16:9"
      beforeInit: "macros/macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      navigation:
        scroll: false
    seal: false
    includes:
      after_body: usfws-logo.html
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
                      fig.retina = 3, fig.align = "center")
options(htmltools.dir.version = FALSE)
if (!requireNamespace("pacman")) install.packages("pacman")

if (!requireNamespace("icon")) remotes::install_github("mitchelloharawild/icon")

# Load all required packages, installing if necessary
pacman::p_load(knitr, icon, tidyverse, crayon, flair, sbtools, mapview, kableExtra,
               leaflet, ggplot2, sf, DT, xaringanthemer, styler, showtext)

# download_fontawesome()  # download the fontawesome icons first time
```

```{r xaringan-themer, include=FALSE, eval=TRUE}
style_mono_light(code_font_family = "Fira Code",
  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css",
  base_font_size = "22px",
  outfile = "css/xaringan-themer.css"
)
```

class: hide-logo, center, middle, inverse
# Holding ourselves accountable for data management: actions in Alaska

.pull-left[
.large[McCrea Cobb]  
Refuge Inventory and Monitoring Program  

.large[Erik Osnas]  
Migratory Bird Management 
]

.pull-right[
.large[Amy Pocewicz]  
Science Applications  

.large[Ryan Wilson]  
Fisheries and Ecological Services
]

<br>
<br>
`r icon::fontawesome("github")` usfws.github.io/data-mgt-accountability


???
Hello and welcome.



---
class: inverse, center, middle, hide-logo
# Outline


???
Ok, what will we be covering today?

---
# Slide title

some text

